---
title: "Reproducible Research: Peer Assessment 1"
author: "Peter Dunham"
date: "February 22, 2016"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

The raw data "activity.csv"  to be included in the GitHub repo.  The file can also be downloaded from:  https://www.coursera.org/learn/reproducible-research/peer/gYyPt/course-project-1

Eitherway, the working directory should be set to the directory that contains "activity.csv"

After setting your working directory:
```{r}
   #getwd('YOUR DIRECTORY PATH HERE')
```

Then you can load activity data using "read.csv"
```{r}
   RawActivity<-read.csv(paste0(getwd(),'/activity.csv'))
```

The following displays a small subset of the data to show how "interval" fields relate to
5 minute intervals in a 24 hour date:
```{r}
   RawActivity[861:868,]
```



## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
